Controlled growth and property measurement of one-dimensional oxide nanostructures for energy applications

### 2015-04-23 misc/paper.tex
mwe update

\ce{H^{\sigma +}}-\ce{Cl^{\delta -}}, polar bond and permanent dipole moment,

@@

@@

@@

>>>>

\cee{H^{\sigma +}}-\cee{Cl^{\delta -}}, polar bond and permanent dipole moment,

@@

\section{EM thesis}

Time domain and parallel distributed integral equation techniques for full--wave microelectronics simulation.\cite{Yang2005a}

time domain integral equations; Modified Nodal Analysis; multi-level low-rank decomposition algorithm;

Surface-based TDIE: incorporating skins effects without volumetric meshing; volume current?

Scalar potential produced on electrically small terminals will be equal to the circuit potential of the circuit node.

edge-based Rao-Wilton-Glisson spatial basis functions: triangular discretization of surface S.

@@

\section{metrology}

Coordinate measurement techniques (CMT).\cite{Goch1990} $L_2$-norm inaccurate in computational fitting of measured points, where Tschebyscheff-norm should be applied. \citeauthor{Goch1990} proposed a universal algorithm based on both $L_2$-norm and T-norm.

reference coordinate system (RCS); coordinate measuring machine (CMM); workpiece-related coordinate system (WCS);

\[
Q_G = (\sum_{i=1}^n [d(x_i, x_S)]^2)^{1/2}
\]
and

\[
Q_T = {sup \atop x_i\in W_I} |d(\vec{x_i}, \vec{x_S})|
\]

subscript $i(I)$ for measured point(surface); subscript $s(S)$ for nominal point(surface).

@@

\subsection{headline and elevator speech}

Aligning with customer priorities
Addressing power sensitive markets
Application benefit, use-case
Is projected /Is positioned
Is here to stay
Offer the best path towards
Cost-effective
